\TitlePt

### 2016-03-16 paper-fatiando.tex
Rename papers with the actual subject, not just number
Needed to reorder the chapters so paper1, etc, didn't make much sense
anymore.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper1/gridding_plotting_contourf}
    \caption{
    Example of 1) generating a random scatter of points (black dots),
    2) using that to make synthetic data, and
    3) automatically gridding and plotting the data using a
    Fatiando a Terra wrapper for the Matplotlib ``contourf``
    function.
    }
    \label{fig:p1-contourf}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper1/gridding_plotting_basemap}
    \caption{
        Example of map plotting with the Robinson projection using the
        Matplotlib Basemap toolkit.
    }
    \label{fig:p1-basemap}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/meshes_3dplotting_2prisms}
    \caption{
        Example of plotting a list of right rectangular prisms in Mayavi.
    }
    \label{fig:p1-twoprisms}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/meshes_3dplotting_mesh}
    \caption{
        Example of generating and visualizing a structured prism mesh.
    }
    \label{fig:p1-mesh}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/meshes_3dplotting_meshtopo}
    \caption{
        Example of generating and visualizing a prism mesh with masked
        topography.
    }
    \label{fig:p1-meshtopo}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/meshes_3dplotting_tesseroid}
    \caption{
        Example of creating a tesseroid (spherical prism) model and visualizing
        it in Mayavi.
    }
    \label{fig:p1-tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/gravmag_tesseroid_data}
    \caption{
        Example of forward modeling the gravity anomaly using the tesseroid
        model shown in Figure~\ref{fig:p1-tesseroid}.
    }
    \label{fig:p1-tesseroidgrav}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/forward_modeling_polyprism_drawing}
    \caption{
        Screen-shot of interactively drawing the contour of a 3D polygonal
        prism, as viewed from above.
    }
    \label{fig:p1-drawing}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/paper1/forward_modeling_polyprism}
    \caption{
        Example of forward modeling the gravity anomaly of a 3D polygonal
        prism.
        a) forward modeled gravity anomaly.
        b) 3D plot of the polygonal prism.
    }
    \label{fig:p1-polyprism}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/gravmag_imaging}
    \caption{
        Example of using the "sandwich model" imaging method to recover a 3D
        image of a geologic body based on its gravity anomaly. The colored
        blocks are a cutoff of the imaged body. The black contours are the true
        source of the gravity anomaly.
    }
    \label{fig:p1-imaging}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/gravmag_harvester_seed}
    \caption{
        The small blue prism is the seed used by
        \texttt{fatiando.gravmag.harvester} to perform the inversion of a
        gravity anomaly. The black contours are the true source of the gravity
        anomaly.
    }
    \label{fig:p1-seed}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper1/gravmag_harvester}
    \caption{
        The blue prisms are the result of a gravity inversion using module
        \texttt{fatiando.gravmag.harvester}. The black contours are the true
        source of the gravity anomaly. Notice how the inversion was able to
        recover the approximate geometry of the true source.
    }
    \label{fig:p1-harvester}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper1/seismic_tomo}
    \caption{
        Example run of a simplified 2D tomography. The top-left panel shows the
        true velocity model with the locations of earthquakes (yellow stars)
        and receivers (green triangles). The top-right panel shows the
        ray-paths between earthquakes and receivers. The bottom-left panel is
        the velocity estimated by the tomography. The bottom-right panel is a
        histogram of the travel-time residuals of the tomography. Notice how
        the majority of residuals are close to 0 s, indicating a good fit to
        the data.
    }
    \label{fig:p1-tomo}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-fatiando/gridding_plotting_contourf}
    \caption{
    Example of 1) generating a random scatter of points (black dots),
    2) using that to make synthetic data, and
    3) automatically gridding and plotting the data using a
    Fatiando a Terra wrapper for the Matplotlib ``contourf``
    function.
    }
    \label{fig:p1-contourf}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-fatiando/gridding_plotting_basemap}
    \caption{
        Example of map plotting with the Robinson projection using the
        Matplotlib Basemap toolkit.
    }
    \label{fig:p1-basemap}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/meshes_3dplotting_2prisms}
    \caption{
        Example of plotting a list of right rectangular prisms in Mayavi.
    }
    \label{fig:p1-twoprisms}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/meshes_3dplotting_mesh}
    \caption{
        Example of generating and visualizing a structured prism mesh.
    }
    \label{fig:p1-mesh}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/meshes_3dplotting_meshtopo}
    \caption{
        Example of generating and visualizing a prism mesh with masked
        topography.
    }
    \label{fig:p1-meshtopo}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/meshes_3dplotting_tesseroid}
    \caption{
        Example of creating a tesseroid (spherical prism) model and visualizing
        it in Mayavi.
    }
    \label{fig:p1-tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/gravmag_tesseroid_data}
    \caption{
        Example of forward modeling the gravity anomaly using the tesseroid
        model shown in Figure~\ref{fig:p1-tesseroid}.
    }
    \label{fig:p1-tesseroidgrav}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/forward_modeling_polyprism_drawing}
    \caption{
        Screen-shot of interactively drawing the contour of a 3D polygonal
        prism, as viewed from above.
    }
    \label{fig:p1-drawing}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/paper-fatiando/forward_modeling_polyprism}
    \caption{
        Example of forward modeling the gravity anomaly of a 3D polygonal
        prism.
        a) forward modeled gravity anomaly.
        b) 3D plot of the polygonal prism.
    }
    \label{fig:p1-polyprism}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/gravmag_imaging}
    \caption{
        Example of using the "sandwich model" imaging method to recover a 3D
        image of a geologic body based on its gravity anomaly. The colored
        blocks are a cutoff of the imaged body. The black contours are the true
        source of the gravity anomaly.
    }
    \label{fig:p1-imaging}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/gravmag_harvester_seed}
    \caption{
        The small blue prism is the seed used by
        \texttt{fatiando.gravmag.harvester} to perform the inversion of a
        gravity anomaly. The black contours are the true source of the gravity
        anomaly.
    }
    \label{fig:p1-seed}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-fatiando/gravmag_harvester}
    \caption{
        The blue prisms are the result of a gravity inversion using module
        \texttt{fatiando.gravmag.harvester}. The black contours are the true
        source of the gravity anomaly. Notice how the inversion was able to
        recover the approximate geometry of the true source.
    }
    \label{fig:p1-harvester}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-fatiando/seismic_tomo}
    \caption{
        Example run of a simplified 2D tomography. The top-left panel shows the
        true velocity model with the locations of earthquakes (yellow stars)
        and receivers (green triangles). The top-right panel shows the
        ray-paths between earthquakes and receivers. The bottom-left panel is
        the velocity estimated by the tomography. The bottom-right panel is a
        histogram of the travel-time residuals of the tomography. Notice how
        the majority of residuals are close to 0 s, indicating a good fit to
        the data.
    }
    \label{fig:p1-tomo}
\end{figure}

### 2016-03-16 paper-moho.tex
Rename papers with the actual subject, not just number
Needed to reorder the chapters so paper1, etc, didn't make much sense
anymore.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper3/problem-concept}
    \caption{
        Sketch of the stages in gravity data correction and
        the discretization of the anomalous Moho relief using tesseroids.
        (a) The Earth and the measured gravity at point P ($g(P)$).
        (b) The Normal Earth and the calculated normal gravity at point P
        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
        (c) The gravity disturbance ($\delta(P)$) and
        the corresponding density anomalies after removal of the normal gravity:
        topography, oceans, crustal heterogeneities, and the anomalous Moho.
        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
        correction and the remaining density anomalies.
        (e) All density anomalies save the anomalous Moho are assumed to have
        been removed before inversion.
        (f) The discretization of the anomalous Moho in tesseroids. Grey
        tesseroids will have a negative density contrast while red tesseroids
        will have a positive one.
    }
    \label{fig:p3-anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/paper3/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015}.
    }
    \label{fig:p3-tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper3/cv-grid-separation}
    \caption{Sketch of a data grid separated into
        the training (white dots with black outlines)
        and testing (black dots) data sets.
        The training data set is still displayed on a regular grid
        but with twice the grid spacing
        of the original data grid.}
    \label{fig:p3-grid_separation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper3/synthetic-simple-data}
    \caption{
        A simple Moho model made of tesseroids for synthetic data application.
        (a) The Moho depth of the model in kilometers.
        The model transitions from a deep Moho in the right to a shallow Moho in
        left, simulating the transition between a continental and an oceanic
        Moho.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model
        shown in (a).
    }
    \label{fig:p3-simple-data}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper3/synthetic-simple-results}
    \caption{
        Results from the inversion of the simple synthetic data.
        (a) The estimated Moho depth.
        (b) The difference between the true model depths
        and the estimated depths.
        (c) The inversion residuals (observed data minus
        the data predicted by the estimate).
        (d) Histogram of the residuals. Also shown are the calculated
        mean and standard deviation (std) of the residuals.
        Note that the data were contaminated with normally distributed
        pseudo-random noise with zero mean and 5 mGal standard deviation.
        (e) Cross-validation curve used to determine the optimal regularization
        parameter (Eq.~\ref{eq:p3-goalfunction}).
        Both axis are in logarithmic scale.
        The minimum Mean Square Error (Eq.~\ref{eq:p3-msemu}) is found at
        $\mu = 0.00046$ (red triangle).
        (f) Goal function value (Eq.~\ref{eq:p3-goalfunction}) per Gauss-Newton
        iteration showing the convergence of the gradient descent.
        The y-axis is in logarithmic scale.
    }
    \label{fig:p3-simple-results}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper3/synthetic-crust1-data}
    \caption{
        Synthetic data of a model derived from CRUST1.0.
        The model is made of tesseroids with an constant density-contrast
        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
        $z_{ref} = 30\ km$.
        (a) The Moho depth of the model in kilometers.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model.
        (c) Synthetic seismic data simulating point estimates of Moho depth.
        The point estimates were obtained by interpolating
        the Moho depth in (a).
    }
    \label{fig:p3-crust1-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper3/synthetic-crust1-results}
    \caption{
        Inversion results from the CRUST1.0 synthetic data.
        (a) Cross-validation curve used to determine
        the regularization parameter (Eq.~\ref{eq:p3-goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:p3-msemu}) is found at
        $\mu = 0.0001$ (red triangle).
        (b) Cross-validation results used to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:p3-msehyper}) in $km^2$.
        The minimum (red triangle) is found at $z_{ref} = 30\ km$
        and $\Delta\rho = 350\ kg/m^3$.
        (c) The estimated Moho depth.
        (d) Difference between the CRUST1.0 model depths
        (Fig.~\ref{fig:p3-crust1-data}a)
        and the estimated depths.
        (e) Histogram of the inversion residuals
        (observed minus predicted data).
        (f) Histogram of the differences between
        the synthetic seismic observations (Fig.~\ref{fig:p3-crust1-data}c)
        and the estimated depths.
        (g) The inversion residuals.
        (h) Difference between the seismic and the estimated depths.
    }
    \label{fig:p3-crust1-results}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper3/south-america-corrections}
    \caption{
        Gravity data for South America and the models used in the data
        corrections.
        (a) The gravity disturbance (Eq.~\ref{eq:p3-disturbance}) calculated from
        the raw gravity data.
        (b) Topography from ETOPO1.
        (c) Gravitational attraction of the topography calculated
        at the observation height using tesseroids.
        (d) The Bouguer disturbance (Eq.~\ref{eq:p3-bouguer}) obtained by
        subtracting (c) from (a).
        The upper (e), middle (f), and lower (g) sediment layer thicknesses
        from the CRUST1.0 model.
        (h) The total gravitational attraction of the sediment layers shown in
        (e), (f), and (g), calculated using tesseroids.
        }
    \label{fig:p3-sam-corrections}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper3/south-america-data}
    \caption{
        Input data for the South American Moho inversion.
        (a) Sediment-free Bouguer disturbance for South America.
        Obtained by subtracting the total sediment gravitational effect
        (Fig.~\ref{fig:p3-sam-corrections}h) from the Bouguer disturbance
        (Fig.~\ref{fig:p3-sam-corrections}d).
        (b) Seismological Moho depth estimates from
        \citet{assumpcao2013a}.
    }
    \label{fig:p3-sam-data}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper3/south-america-cv}
    \caption{
        Cross-validation results for the South American Moho inversion.
        (a) Cross-validation to determine the regularization parameter $\mu$
        (Eq.~\ref{eq:p3-goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:p3-msemu}),
        shown as a red triangle,
        corresponds to $\mu = 10^{-10}$.
        (b) Cross-validation to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:p3-msehyper}).
        The minimum (red triangle) is found at $z_{ref} = 35\ km$
        and $\Delta\rho = 400\ kg/m^3$.
    }
    \label{fig:p3-sam-cv}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper3/south-america-moho}
    \caption{
        Inversion results for the South American Moho.
        (a) The estimated Moho depth of South America.
        The solid light grey line is the 35 km Moho depth contour.
        (b) Inversion residuals (observed data in Fig.~\ref{fig:p3-sam-data}a
        minus the data predicted by the estimate (a)).
        (c) Differences between the seismological depths of
        \citet{assumpcao2013a} and our gravity-derived estimate shown in (a).
        The inset in (c) shows a histogram of the differences along with their
        calculated mean and standard deviation (std).
    }
    \label{fig:p3-sam-moho}
\end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/paper-moho/problem-concept}
    \caption{
        Sketch of the stages in gravity data correction and
        the discretization of the anomalous Moho relief using tesseroids.
        (a) The Earth and the measured gravity at point P ($g(P)$).
        (b) The Normal Earth and the calculated normal gravity at point P
        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
        (c) The gravity disturbance ($\delta(P)$) and
        the corresponding density anomalies after removal of the normal gravity:
        topography, oceans, crustal heterogeneities, and the anomalous Moho.
        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
        correction and the remaining density anomalies.
        (e) All density anomalies save the anomalous Moho are assumed to have
        been removed before inversion.
        (f) The discretization of the anomalous Moho in tesseroids. Grey
        tesseroids will have a negative density contrast while red tesseroids
        will have a positive one.
    }
    \label{fig:p3-anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/paper-moho/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015}.
    }
    \label{fig:p3-tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper-moho/cv-grid-separation}
    \caption{Sketch of a data grid separated into
        the training (white dots with black outlines)
        and testing (black dots) data sets.
        The training data set is still displayed on a regular grid
        but with twice the grid spacing
        of the original data grid.}
    \label{fig:p3-grid_separation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper-moho/synthetic-simple-data}
    \caption{
        A simple Moho model made of tesseroids for synthetic data application.
        (a) The Moho depth of the model in kilometers.
        The model transitions from a deep Moho in the right to a shallow Moho in
        left, simulating the transition between a continental and an oceanic
        Moho.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model
        shown in (a).
    }
    \label{fig:p3-simple-data}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-moho/synthetic-simple-results}
    \caption{
        Results from the inversion of the simple synthetic data.
        (a) The estimated Moho depth.
        (b) The difference between the true model depths
        and the estimated depths.
        (c) The inversion residuals (observed data minus
        the data predicted by the estimate).
        (d) Histogram of the residuals. Also shown are the calculated
        mean and standard deviation (std) of the residuals.
        Note that the data were contaminated with normally distributed
        pseudo-random noise with zero mean and 5 mGal standard deviation.
        (e) Cross-validation curve used to determine the optimal regularization
        parameter (Eq.~\ref{eq:p3-goalfunction}).
        Both axis are in logarithmic scale.
        The minimum Mean Square Error (Eq.~\ref{eq:p3-msemu}) is found at
        $\mu = 0.00046$ (red triangle).
        (f) Goal function value (Eq.~\ref{eq:p3-goalfunction}) per Gauss-Newton
        iteration showing the convergence of the gradient descent.
        The y-axis is in logarithmic scale.
    }
    \label{fig:p3-simple-results}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-moho/synthetic-crust1-data}
    \caption{
        Synthetic data of a model derived from CRUST1.0.
        The model is made of tesseroids with an constant density-contrast
        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
        $z_{ref} = 30\ km$.
        (a) The Moho depth of the model in kilometers.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model.
        (c) Synthetic seismic data simulating point estimates of Moho depth.
        The point estimates were obtained by interpolating
        the Moho depth in (a).
    }
    \label{fig:p3-crust1-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-moho/synthetic-crust1-results}
    \caption{
        Inversion results from the CRUST1.0 synthetic data.
        (a) Cross-validation curve used to determine
        the regularization parameter (Eq.~\ref{eq:p3-goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:p3-msemu}) is found at
        $\mu = 0.0001$ (red triangle).
        (b) Cross-validation results used to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:p3-msehyper}) in $km^2$.
        The minimum (red triangle) is found at $z_{ref} = 30\ km$
        and $\Delta\rho = 350\ kg/m^3$.
        (c) The estimated Moho depth.
        (d) Difference between the CRUST1.0 model depths
        (Fig.~\ref{fig:p3-crust1-data}a)
        and the estimated depths.
        (e) Histogram of the inversion residuals
        (observed minus predicted data).
        (f) Histogram of the differences between
        the synthetic seismic observations (Fig.~\ref{fig:p3-crust1-data}c)
        and the estimated depths.
        (g) The inversion residuals.
        (h) Difference between the seismic and the estimated depths.
    }
    \label{fig:p3-crust1-results}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-moho/south-america-corrections}
    \caption{
        Gravity data for South America and the models used in the data
        corrections.
        (a) The gravity disturbance (Eq.~\ref{eq:p3-disturbance}) calculated from
        the raw gravity data.
        (b) Topography from ETOPO1.
        (c) Gravitational attraction of the topography calculated
        at the observation height using tesseroids.
        (d) The Bouguer disturbance (Eq.~\ref{eq:p3-bouguer}) obtained by
        subtracting (c) from (a).
        The upper (e), middle (f), and lower (g) sediment layer thicknesses
        from the CRUST1.0 model.
        (h) The total gravitational attraction of the sediment layers shown in
        (e), (f), and (g), calculated using tesseroids.
        }
    \label{fig:p3-sam-corrections}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-moho/south-america-data}
    \caption{
        Input data for the South American Moho inversion.
        (a) Sediment-free Bouguer disturbance for South America.
        Obtained by subtracting the total sediment gravitational effect
        (Fig.~\ref{fig:p3-sam-corrections}h) from the Bouguer disturbance
        (Fig.~\ref{fig:p3-sam-corrections}d).
        (b) Seismological Moho depth estimates from
        \citet{assumpcao2013a}.
    }
    \label{fig:p3-sam-data}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper-moho/south-america-cv}
    \caption{
        Cross-validation results for the South American Moho inversion.
        (a) Cross-validation to determine the regularization parameter $\mu$
        (Eq.~\ref{eq:p3-goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:p3-msemu}),
        shown as a red triangle,
        corresponds to $\mu = 10^{-10}$.
        (b) Cross-validation to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:p3-msehyper}).
        The minimum (red triangle) is found at $z_{ref} = 35\ km$
        and $\Delta\rho = 400\ kg/m^3$.
    }
    \label{fig:p3-sam-cv}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-moho/south-america-moho}
    \caption{
        Inversion results for the South American Moho.
        (a) The estimated Moho depth of South America.
        The solid light grey line is the 35 km Moho depth contour.
        (b) Inversion residuals (observed data in Fig.~\ref{fig:p3-sam-data}a
        minus the data predicted by the estimate (a)).
        (c) Differences between the seismological depths of
        \citet{assumpcao2013a} and our gravity-derived estimate shown in (a).
        The inset in (c) shows a histogram of the differences along with their
        calculated mean and standard deviation (std).
    }
    \label{fig:p3-sam-moho}
\end{figure*}

### 2016-03-16 paper-tesseroids.tex
Rename papers with the actual subject, not just number
Needed to reorder the chapters so paper1, etc, didn't make much sense
anymore.

\begin{figure}
    \centering
    \includegraphics{figures/paper2/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:p2-tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/paper2/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature.
        Black circles represent the horizontal location of the point masses.
        a) $g_{xy}$ calculated at $400\ km$ height using GLQ order 2
        ($2 \times 2 \times 2 = 8$ point masses).
        b) At $150\ km$ height and GLQ order 2,
        the result resembles that of
        four point masses instead of a single tesseroid.
        This effect was shown by \citet{ku1977}.
        c) At $150\ km$ but with a higher GLQ order of 30.
        In (c) the horizontal locations of the point masses were not shown.
        Notice that the results shown in (c) are similar to that expected
        for a single mass source.
    }
    \label{fig:p2-glqerrorsample}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper2/tesseroid-split}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using the distance-size ratio $D$ equal to
        (b) 1, (c) 2, and (d) 6.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
        Note that increasing $D$
        results in a fine division of the tesseroid
        close the computation point
        and a coarser division further away.
    }
    \label{fig:p2-division}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper2/distance-size-curves}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models and computation
        grids shown in Table~\ref{tbl:experiment}.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:p2-dist-size-curves}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/paper2/gzz-with-height}
    \caption{
        Difference between the computed $g_{zz}$ for the spherical shell and
        the tesseroid model at different heights. Curves show the maximum
        difference as a percentage of the shell value.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:p2-gzz-with-height}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/paper-tesseroids/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
    }
    \label{fig:p2-tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/paper-tesseroids/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature.
        Black circles represent the horizontal location of the point masses.
        a) $g_{xy}$ calculated at $400\ km$ height using GLQ order 2
        ($2 \times 2 \times 2 = 8$ point masses).
        b) At $150\ km$ height and GLQ order 2,
        the result resembles that of
        four point masses instead of a single tesseroid.
        This effect was shown by \citet{ku1977}.
        c) At $150\ km$ but with a higher GLQ order of 30.
        In (c) the horizontal locations of the point masses were not shown.
        Notice that the results shown in (c) are similar to that expected
        for a single mass source.
    }
    \label{fig:p2-glqerrorsample}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/paper-tesseroids/tesseroid-split}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using the distance-size ratio $D$ equal to
        (b) 1, (c) 2, and (d) 6.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
        Note that increasing $D$
        results in a fine division of the tesseroid
        close the computation point
        and a coarser division further away.
    }
    \label{fig:p2-division}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/paper-tesseroids/distance-size-curves}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models and computation
        grids shown in Table~\ref{tbl:experiment}.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:p2-dist-size-curves}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/paper-tesseroids/gzz-with-height}
    \caption{
        Difference between the computed $g_{zz}$ for the spherical shell and
        the tesseroid model at different heights. Curves show the maximum
        difference as a percentage of the shell value.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:p2-gzz-with-height}
\end{figure}
